My title

### 2024-03-16 paper/paper.qmd
updated model section

# 1.0 Introduction

@@

## 1.1 Importing Important Packages.
In this analysis, we employ a range of R [@citeR] packages tailored for data cleaning, transformation, analysis, and reporting. `Tidyverse` by @tidyverse is used for data wrangling, `janitor` package by @janitor is used for data cleaning operations, and `knitr` by @knitr for data presentation in data tables.The following code section aims at importing the important packages that are essential for examining the missing values in the data set.We run the model in R @citeR using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. For comprehensive mixed effects model analysis, we leverage the `broom.mixed` package [@broommixed], which extends the `broom` package functionalities to mixed models, facilitating the extraction, tidying, and representation of model outputs. Furthermore, the `modelsummary` package [@modelsummary] provides tools for creating customizable summary tables of model results, enhancing the interpretability and dissemination of statistical findings. By calculating the LOO-CV scores for different models with `loo` [@loo], we could compare them based on their out-of-sample predictive accuracy. Lower values of LOOIC indicate better model performance. The following code sections aim to import these crucial packages, essential for conducting a thorough analysis and addressing the research questions at hand, while ensuring data integrity and transparent reporting of results.

@@

# 2.0 Data {#sec-data}

@@

## 2.1 Data Sources
The Alberta Government created the dataset.The official website of the Government of Alberta provides a single platform for services and information pertaining to Alberta, Canada. It provides information on government news, jobs, social services, health, and education, making it an essential tool for both locals and tourists to be updated about provincial issues.

## 2.2 Variables
Order by total number of deaths and a ranking of the top 30 causes of death in Alberta each year.Our table lists the top eight causes of death in Alberta in 2022. Examine each variable in detail:
*Year*: This denotes the data gathering year, which for all entries is 2022.
*Cause*: This represents the medical condition or event that led to death. The causes listed are shown in @fig-dataset-overview:
`Organic dementia`
`All other forms of chronic...`, 
`Other ill-defined and unknown...`, 
`COVID-19, virus identified`, 
`Malignant neoplasms of the trachea, bronchus, and lung`, 
`Acute myocardial infarction`, 
`Accidental poisoning by and...`, 
`Other chronic obstructive pulmonary diseases`, 
*Ranking*: This is a ranking by the number of deaths caused by each disease, with 1 being the highest.
*Deaths*: The number of deaths attributed to each cause.
*Year*: Indicates the number of years in which data was collected for that reason.

@@

## 2.3 Data Description
It accurately reflects health issues specific to the region, but this information is somewhat limited by location. Health policies vary from country to country, and in some regions and countries, health coverage may be less developed than in others, and low-income groups may not be able to afford basic medical care, which increases their risk of chronic diseases and other health problems. The main types of employment in a city also have an impact on health; In an industrial city, some jobs may require exposure to hazardous substances or strenuous physical labor, which increases the likelihood of developing occupational diseases. Risks associated with the workplace may lead to an increase in diseases such as cardiovascular and respiratory diseases. In addition, communities with higher levels of education and economic prosperity generally have stronger social support systems, which are critical for disease prevention.

@@

# 3.0 Model

## 3.1 Model setup:

@@

## 3.2 Model justification

Based on the models discussed above, it is challenging to determine whether each cause of death has a positive or negative correlation with the total number of deaths, as the leading cause of death changes each year. The specific impact of these changes must be determined by the coefficient of each leading cause of death to decide whether the correlation is positive or negative. According to Table 1, from 2001 to 2022, organic dementia shows an upward trend, indicating that organic dementia is positively correlated with the total number of deaths. In the upcoming model results section, we will elaborate in detail on the association between each cause of death and the total number of deaths.

@@

>>>>

# Introduction

@@

## Importing Important Packages.
In this analysis, we employ a range of R [@citeR] packages tailored for data cleaning, transformation, analysis, and reporting. `Tidyverse` by @tidyverse is used for data wrangling, `janitor` package by @janitor is used for data cleaning operations, and `knitr` by @knitr for data presentation in data tables.The following code section aims at importing the important packages that are essential for examining the missing values in the data set.We run the model in R @citeR using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. For comprehensive mixed effects model analysis, we leverage the `broom.mixed` package [@broommixed], which extends the `broom` package functionalities to mixed models, facilitating the extraction, tidying, and representation of model outputs. Furthermore, the `modelsummary` package [@modelsummary] provides tools for creating customizable summary tables of model results, enhancing the interpretability and dissemination of statistical findings. By calculating the LOO-CV scores for different models with `loo` [@loo], we could compare them based on their out-of-sample predictive accuracy. Lower values of LOOIC indicate better model performance. The following code sections aim to import these crucial packages, essential for conducting a thorough analysis and addressing the research questions at hand, while ensuring data integrity and transparent reporting of results.

@@

# Data {#sec-data}

@@

## Data Sources
The Alberta Government created the dataset.The official website of the Government of Alberta provides a single platform for services and information pertaining to Alberta, Canada. It provides information on government news, jobs, social services, health, and education, making it an essential tool for both locals and tourists to be updated about provincial issues.

## Variables
Order by total number of deaths and a ranking of the top 30 causes of death in Alberta each year.Our table lists the top eight causes of death in Alberta in 2022. Examine each variable in detail:
*Year*: This denotes the data gathering year, which for all entries is 2022.
*Cause*: This represents the medical condition or event that led to death. The causes listed are shown in @fig-dataset-overview:
`Organic dementia`
`All other forms of chronic...`, 
`Other ill-defined and unknown...`, 
`COVID-19, virus identified`, 
`Malignant neoplasms of the trachea, bronchus, and lung`, 
`Acute myocardial infarction`, 
`Accidental poisoning by and...`, 
`Other chronic obstructive pulmonary diseases`, 
*Ranking*: This is a ranking by the number of deaths caused by each disease, with 1 being the highest.
*Deaths*: The number of deaths attributed to each cause.
*Year*: Indicates the number of years in which data was collected for that reason.

@@

## Data Description
It accurately reflects health issues specific to the region, but this information is somewhat limited by location. Health policies vary from country to country, and in some regions and countries, health coverage may be less developed than in others, and low-income groups may not be able to afford basic medical care, which increases their risk of chronic diseases and other health problems. The main types of employment in a city also have an impact on health; In an industrial city, some jobs may require exposure to hazardous substances or strenuous physical labor, which increases the likelihood of developing occupational diseases. Risks associated with the workplace may lead to an increase in diseases such as cardiovascular and respiratory diseases. In addition, communities with higher levels of education and economic prosperity generally have stronger social support systems, which are critical for disease prevention.

@@

# Model

## Model setup:

@@

## Model justification

Based on the models discussed above, it is challenging to determine whether each cause of death has a positive or negative correlation with the total number of deaths, as the leading cause of death changes each year. The specific impact of these changes must be determined by the coefficient of each leading cause of death to decide whether the correlation is positive or negative. According to @fig-planes, from 2001 to 2022, organic dementia shows an upward trend, indicating that organic dementia is positively correlated with the total number of deaths. In the upcoming model results section, we will elaborate in detail on the association between each cause of death and the total number of deaths.

@@

```{r}
#| label: tbl-mean-var
#| tbl-cap: Comparison of Mean and Variance of Total Death in from 2001 to 2022
#| echo: false
#| warning: false
# Calculate the mean and variance
summary_stats <- alberta_cod %>%
  summarise(
    Mean = mean(total_deaths, na.rm = TRUE),  # Calculate mean, remove NA values if any
    Variance = var(total_deaths, na.rm = TRUE) # Calculate variance, remove NA values if any
  )

# Create a table
kable(summary_stats, caption = "Comparison of Mean and Variance of Total Deaths")
